---
output: 
  html_document:
    fig_caption: yes
    css: www/webstyles.css
    anchor_sections: FALSE
    includes: 
      in_header: "header_manual.html" 
      after_body: "footer.html"
    self_contained: yes
title: "NETN water summary"
params:
  park: MABI # 4-letter park code
  year_start: 2006 # first year of data
  year_current: 2023 # current year of data
---

```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.pos = "h", warning = FALSE, message = FALSE)
```

```{r include = F, results = 'hide'}
library(tidyverse)
library(waterNETN)
library(leaflet)
library(grid)
library(gridExtra)
library(kableExtra)
#library(plotly)
```
```{r results = 'hide', cache = T, eval = F}
importData()
```

```{r }
# park = "ACAD"; yr_start = 2006; yr_current = 2023;
parkcode <- "ACAD" #child_env$park
# park = parkcode
# yr_start <- params$year_start
# yr_current <- params$year_current
# yr_prev <- yr_current - 1

site_df <- unique(getEvents(park = "ACAD", years = yr_current)[, c("SiteCode", "SiteName", "UnitCode", "UnitName", "SiteType")])
#site_df <- getSites(park = parkcode)[,c("SiteCode", "SiteName", "UnitCode", "UnitName")]
site_list <- unique(site_df$SiteCode)
park_name <- unique(site_df$UnitName)
site_name <- unique(site_df$SiteName)
lake_list <- site_df$SiteCode[site_df$SiteType == "Lake"]
stream_list <- site_df$SiteCode[site_df$SiteType == "Stream"]
eval_stream <- if(!is.null(stream_list)){TRUE} else {FALSE}
eval_lake <- if(!is.null(lake_list)){TRUE} else {FALSE}

source("fake_bands_legend_code.R") # for legend called legg
```



## ACAD {.tabset}
### Lakes {.tabset}
<!-- Plots for lakes only -->
#### Water Quality  {.tabset}
##### Status {.tabset}
```{r warning = FALSE, message = FALSE, results = 'asis', fig.height=9, fig.width=13}
for(i in seq_along(lake_list)){
  lakecode <- lake_list[[i]]
  sitename <- site_df$SiteName[site_df$SiteCode==lakecode]
  sitecode <- site_df$SiteCode[site_df$SiteCode==lakecode]
  cat("###### ", sitename, "{.tabset} \n\n")
  cat("\n\n")
  cat("<details open><summary class = 'drop'>Field Measurements</summary>", "\n\n")
  cat(paste0("<h1>Historic (", yr_start, " to ", yr_prev, ") vs. Current (", yr_current, ")</h1>\n\n"))

  <<waterbandp_chunk>>
  
  cat(paste0(
  "<p style='width:1280px;'>",
  'The plots above show historic ranges for ', sitename, 
   ' based on the range of measurements collected from ',
   yr_start, ' to ', yr_prev, ' for each month. The outermost band represents the
   historic maximum and minimum value collected for each month.
   The second inner band represents the 95% range of historic values
   by month. The innermost band represents the 50% range of historic
   values by month. The points represent the most 
   recent measurements collected in ', yr_current, ' by month. 
   Water quality thresholds are derived from state surface water quality 
   standards. Parameter abbreviations and additional information are
   defined in "About the Data".</p>\n\n'))
  cat("</details><br>\n")
  
  cat("\n\n")
  
  cat("<details open><summary class = 'drop'>Lab Chemistry</summary>", "\n\n")
  cat(paste0("<h1>Historic (", yr_start, " to ", yr_prev, ") vs. Current (", yr_current, ")</h1>\n\n"))

  <<waterbandn_chunk>>
  
  cat(paste0(
  "<p style='width:1280px;'>",
  'The plots above show historic ranges for ', sitename, 
   ' based on the range of measurements collected from ',
   yr_start, ' to ', yr_prev, ' for each month. The outermost band represents the
   historic maximum and minimum value collected for each month.
   The second inner band represents the 95% range of historic values
   by month. The innermost band represents the 50% range of historic
   values by month. The points represent the most 
   recent measurements collected in ', yr_current, ' by month. 
   Water quality thresholds are derived from state surface water quality 
   standards. Parameter abbreviations and additional information are
   defined in "About the Data".</p>\n\n'))
  cat("</details><br>\n\n")
  
}
```
<br>

##### Trends {.tabset}
```{r warning = F, message = F, fig.height=9, fig.width=13, results = 'asis'}
sonde_params <- c("DO_mgL", "pH", "Temp_F", "SpCond_uScm")
chem_params <- c("TN_mgL", "TP_ugL", "ANC_ueqL")#, "ChlA_ugL")

cat("<details open><summary class = 'drop'>Field Measurements</summary>", "\n\n")
plotTrend(park = parkcode, site = lake_list, years = yr_start:yr_current, parameter = sonde_params, 
          smooth = T, span = 0.5, legend_position = "bottom", threshold = F, numcol = 2)

cat(paste0("<p style='width:1280px;'>Trends in field water quality parameters for ", sitename, " from ",
           yr_start, " to ", yr_current, ". Points represent monthly sample measurements.", 
           " Lines represent loess smoothed trends with span 0.5.</p></details>\n\n"))

cat("\n\n")

cat("<details open><summary class = 'drop'>Lab Chemistry</summary>", "\n\n")
plotTrend(park = parkcode, site = lake_list, years = yr_start:yr_current, parameter = chem_params, 
          smooth = T, span = 0.5, legend_position = "bottom", threshold = F, numcol = 2)

cat(paste0("<p style='width:1280px;'>Trends in lab chemistry water quality parameters for ", sitename, " from ",
           yr_start, " to ", yr_current, ". Points represent monthly sample measurements.", 
           " Lines represent loess smoothed trends with span 0.5.</p></details>\n\n"))
```

#### Water Quantity {.tabset}
##### Status

```{r warning = F, message = FALSE, eval = eval_lake, results = 'asis', fig.height=7, fig.width=13}
cat("<details open><summary class='drop'>Lake Water Level</summary>")

plot_lname <- ifelse(length(lake_list) == 1, 
                     site_df$SiteName[site_df$SiteCode == lake_list], 
                     park_name)

plotWaterBands(park = parkcode, site = lake_list, year_current = yr_current, 
               years_historic = yr_start:yr_prev, parameter = "WaterLevel_Feet", 
               facet_scales = "free_y")

cat(paste0(
  "<p style='width:1280px;'>",
  'Historic ranges in water level for ', plot_lname, 
   ' based on the range of measurements collected from ',
   yr_start, ' to ', yr_prev, ' for each month. The outermost band represents the
   historic maximum and minimum value collected for each month.
   The second inner band represents the 95% range of historic values
   by month. The innermost band represents the 50% range of historic
   values by month. The points represent the most 
   recent measurements collected in ', yr_current, ' by month. </p>\n\n'))
  cat("</details><br>\n\n")
```

##### Trends
```{r warning = F, message = FALSE, eval = eval_lake, results = 'asis', fig.height=7, fig.width=13}
cat("<details open><summary class='drop'>Lake Water Level</summary>")

plot_lname <- ifelse(length(lake_list) == 1, site_df$SiteName[site_df$SiteCode == lake_list], 
                     park_name)

plotTrend(park = parkcode, site = lake_list, months = 5:10,
          years = 2013:yr_current, parameter = "WaterLevel_Feet", span = 0.5, gridlines = "grid_x",
          legend_position = 'right')

cat(paste0(
  "<p style='width:1280px;'>",
  'Trends in water level for ', plot_lname, 
   ' from 2013 to ', yr_current, ' for each month. Points represent monthly sample measurements. Lines represent loess smoothed trends with span 0.5.</p>\n\n'))
```
<br>
```{r warning = F, message = FALSE, eval = eval_lake, results = 'asis', fig.height=3, fig.width=13}
plotClimTrend(park = parkcode, years = 2013:yr_current, parameter = 'ppt', palette = c("Set2"), 
              months = 5:10, layers = 'bar', gridlines = "grid_x", units = "eng")
cat(paste0(
  "<p style='width:1280px;'>",
  'Trends in monthly precipitation from May to October for ', plot_lname, 
   ' from 2013 to ', yr_current, '.</p>\n\n'))

```
</details><br>

#### Lake Profiles {.tabset}
```{r}
param_list <- c("DO_mgL", "Temp_F", "pH", "SpCond_uScm", "ChlA_ugL")#, "Turbidity_FNU")
param_name <- c("Dissolved Oxygen (mgL)", "Temperature (C)", "pH", "Specific Conductance (uScm)",
                "Chlorophyll A (ugL)")#, "Turbidity (FNU)")
palette_list <- c("RdYlBu", "RdYlBu", "RdYlBu", "RdYlBu", "RdYlBu")
palette_rev <- c(TRUE, FALSE, TRUE, FALSE, FALSE)
param_df <- data.frame(param = param_list, param_name = param_name, pal = palette_list, rev = palette_rev)
```

##### Status

```{r results = 'asis', fig.height = 9, fig.width = 13}
for(i in seq_along(param_list)){
  param = param_df$param[[i]]
  pal = param_df$pal[param_df$param == param]
  rev = param_df$rev[param_df$param == param]
  param_name = param_df$param_name[param_df$param == param]

  <<prof_stat>>
}
```

##### Trends {.tabset}

```{r results = 'asis', fig.height = 9, fig.width = 13}
for(i in seq_along(lake_list)){
  sitecode = lake_list[[i]]
  cat("###### ", sitecode, "\n\n")
  for(j in seq_along(param_list)){
  param = param_df$param[[j]]
  pal = param_df$pal[param_df$param == param]
  rev = param_df$rev[param_df$param == param]
  param_name = param_df$param_name[param_df$param == param]
  
  <<prof_trend>>
    
  }
}
```


#### Sampling History {.tabset}
```{r}
samp_hist <- sumEvents(park = parkcode, site_type ='lake', years = yr_start:yr_current) |> 
  select(SiteName, param_type:Oct_cens) |> 
  arrange(SiteName, param_type, Parameter)

samp_tab <- 
  kable(samp_hist, format = 'html', align = c(rep("l", 3), rep("c", 13)),
        col.names = c("Site Name", "Param. Type", "Parameter", "Year Range",
                      "# Years Sampled", "May", "Jun", "Jul", "Aug", "Sep", "Oct",
                      "May cens.", "Jun cens.", "Jul cens.", "Aug cens.", "Sep cens.", "Oct cens.")) |> 
  kable_styling(fixed_thead = TRUE, bootstrap_options = c('condensed'), full_width = FALSE,
               position = 'left', font_size = 11) |> 
  collapse_rows(1:2, valign = 'top') 

samp_tab
```


<!-- Plots for streams only -->
### Streams {.tabset}
#### Water Quality  {.tabset}
##### Status {.tabset}

```{r warning = FALSE, message = FALSE, results = 'asis', fig.height=9, fig.width=13}
for(i in seq_along(stream_list)){
  streamcode <- stream_list[[i]]
  sitename <- site_df$SiteName[site_df$SiteCode==streamcode]
  sitecode <- site_df$SiteCode[site_df$SiteCode==streamcode]
  cat("###### ", sitename, "{.tabset} \n\n")
  cat("\n\n")
  cat("<details open><summary class = 'drop'>Field Measurements</summary>", "\n\n")
  cat(paste0("<h1>Historic (", yr_start, " to ", yr_prev, ") vs. Current (", yr_current, ")</h1>\n\n"))

  <<waterbandp_chunk>>
  
  cat(paste0(
  "<p style='width:1280px;'>",
  'The plots above show historic ranges for ', sitename, 
   ' based on the range of measurements collected from ',
   yr_start, ' to ', yr_prev, ' for each month. The outermost band represents the
   historic maximum and minimum value collected for each month.
   The second inner band represents the 95% range of historic values
   by month. The innermost band represents the 50% range of historic
   values by month. The points represent the most 
   recent measurements collected in ', yr_current, ' by month. 
   Water quality thresholds are derived from state surface water quality 
   standards. Parameter abbreviations and additional information are
   defined in "About the Data".</p>\n\n'))
  cat("</details><br>\n")
  
  cat("\n\n")
  
  cat("<details open><summary class = 'drop'>Lab Chemistry</summary>", "\n\n")
  cat(paste0("<h1>Historic (", yr_start, " to ", yr_prev, ") vs. Current (", yr_current, ")</h1>\n\n"))

  <<waterbandn_chunk>>
  
  cat(paste0(
  "<p style='width:1280px;'>",
  'The plots above show historic ranges for ', sitename, 
   ' based on the range of measurements collected from ',
   yr_start, ' to ', yr_prev, ' for each month. The outermost band represents the
   historic maximum and minimum value collected for each month.
   The second inner band represents the 95% range of historic values
   by month. The innermost band represents the 50% range of historic
   values by month. The points represent the most 
   recent measurements collected in ', yr_current, ' by month. 
   Water quality thresholds are derived from state surface water quality 
   standards. Parameter abbreviations and additional information are
   defined in "About the Data".</p>\n\n'))
  cat("</details><br>\n\n")
  
}
```
<br>

##### Trends {.tabset}
```{r warning = F, message = F, fig.height=9, fig.width=13, results = 'asis'}
sonde_params <- c("DO_mgL", "pH", "Temp_F", "SpCond_uScm")
chem_params <- c("TN_mgL", "TP_ugL", "ANC_ueqL")#, "ChlA_ugL")

cat("<details open><summary class = 'drop'>Field Measurements</summary>", "\n\n")
plotTrend(park = parkcode, site = stream_list, years = yr_start:yr_current, parameter = sonde_params, 
          smooth = T, span = 0.5, legend_position = "bottom", threshold = F, numcol = 2)

cat(paste0("<p style='width:1280px;'>Trends in field water quality parameters for ", sitename, " from ",
           yr_start, " to ", yr_current, ". Points represent monthly sample measurements.", 
           " Lines represent loess smoothed trends with span 0.5.</p></details>\n\n"))

cat("\n\n")

cat("<details open><summary class = 'drop'>Lab Chemistry</summary>", "\n\n")
plotTrend(park = parkcode, site = stream_list, years = yr_start:yr_current, parameter = chem_params, 
          smooth = T, span = 0.5, legend_position = "bottom", threshold = F, numcol = 2)

cat(paste0("<p style='width:1280px;'>Trends in lab chemistry water quality parameters for ", sitename, " from ",
           yr_start, " to ", yr_current, ". Points represent monthly sample measurements.", 
           " Lines represent loess smoothed trends with span 0.5.</p></details>\n\n"))
```

#### Water Quantity {.tabset}
##### Status

```{r warning = F, message = FALSE, eval = eval_stream, results = 'asis', fig.height=7, fig.width=13}
plot_sname <- ifelse(length(stream_list) == 1, site_df$SiteName[site_df$SiteCode == stream_list], 
                     park_name)

cat("<details open><summary class='drop'>Discharge vs. Precipitation</summary>")
plotPrecipDischarge(park = parkcode, site = stream_list, years = yr_current)
cat(paste0("<p style='width:1280px;'>Monthly discharge vs. Daily precipitation for ", yr_current, 
    " in ", plot_sname, "</p>"))
cat("</details>\n\n")
```
<br>

##### Trends

```{r warning = F, message = FALSE, eval = eval_stream, results = 'asis', fig.height=7, fig.width=13}
plot_sname <- ifelse(length(stream_list) == 1, site_df$SiteName[site_df$SiteCode == stream_list], 
                     park_name)

cat("<details open><summary class='drop'>Discharge</summary>")
plotTrend(park = parkcode, site = stream_list, years = yr_start:yr_current, parameter = "Discharge_cfs", 
          gridlines = "grid_x", months = 5:10, legend_position = "right")
cat(paste0("<p style='width:1280px;'>Trends in monthly discharge for ", yr_start, " to ", yr_current, 
    " in ", plot_sname, "</p>"))
```
<br>
```{r warning = F, message = FALSE, eval = eval_stream, results = 'asis', fig.height=3, fig.width=13}
plotClimTrend(park = parkcode, years = yr_start:yr_current, parameter = 'ppt', 
              palette = c("Set2"), months = 5:10, layers = 'bar', gridlines = "grid_x", units = "eng")
cat(paste0(
  "<p style='width:1280px;'>",
  'Trends in monthly precipitation from May - October for ', plot_sname, 
   ' from ',
   yr_start, ' to ', yr_current, '.</p>\n\n'))
```
</details><br>

#### Sampling History
```{r}
samp_hist <- sumEvents(park = parkcode, site_type = "stream", years = yr_start:yr_current) |> 
  select(SiteName, param_type:Oct_cens) |> 
  arrange(SiteName, param_type, Parameter)

samp_tab <- 
  kable(samp_hist, format = 'html', align = c(rep("l", 3), rep("c", 13)),
        col.names = c("Site Name", "Param. Type", "Parameter", "Year Range",
                      "# Years Sampled", "May", "Jun", "Jul", "Aug", "Sep", "Oct",
                      "May cens.", "Jun cens.", "Jul cens.", "Aug cens.", "Sep cens.", "Oct cens.")) |> 
  kable_styling(fixed_thead = TRUE, bootstrap_options = c('condensed'), full_width = FALSE,
               position = 'left', font_size = 11) |> 
  collapse_rows(1:2, valign = 'top') 

samp_tab
```

### Climate {.tabset}

```{r}
yr5 = yr_current - 4
drgt_cumppt_cap1 <- paste0("<p style = 'width:1280px;'>Weekly drought condition for ", yr_current, " based on proportion of a park's predominant county in each drought level using the <a href='https://droughtmonitor.unl.edu/'>U.S. Drought Monitor</a> (left). Cumulative annual precipitation in ", yr_current, " by month compared to the 20th century baseline (right). Total monthly precipitation data are derived from  <a href='https://www.ncei.noaa.gov/access/metadata/landing-page/bin/iso?id=gov.noaa.ncdc:C00332'>NOAA monthly NClimGrid gridded climate data</a> extracted for a given park's geographic centroid.</p>") 

anom_comp_cap1 <- paste0("<p style = 'width:1280px;'>Current (", yr_current, ") monthly climate data (solid) with historic baselines (dashed; left). Monthly deviations from historic baselines in ", yr_current, " with positive (red) bars indicating above average deviations, and negative (blue) bars indicating below average deviations (right). Historic baselines are based on <a href='https://www.ncei.noaa.gov/products/land-based-station/us-climate-normals'>NOAA 20th century normals</a> for a given park's geographic centroid. Current monthly data are derived from <a href='https://www.ncei.noaa.gov/access/metadata/landing-page/bin/iso?id=gov.noaa.ncdc:C00332'>NOAA NClimGrid </a> gridded climate dataset extracted for a given park's geographic centroid.</p>") 

anom_cap5 <- paste0("<p style = 'width:1280px;'>Monthly deviations from historic baselines for past 5 years (", yr5, ":", yr_current, ") with positive (red) bars, indicated above average deviations, and negative (blue) bars indicating below average deviations. Historic baselines are based on <a href='https://www.ncei.noaa.gov/products/land-based-station/us-climate-normals'>NOAA 20th century normals</a> for a given park's geographic centroid. 5-year  (", yr5, ":", yr_current, ") monthly data are derived from <a href='https://www.ncei.noaa.gov/access/metadata/landing-page/bin/iso?id=gov.noaa.ncdc:C00332'>NOAA NClimGrid </a> gridded climate dataset extracted for a given park's geographic centroid.</p>")

cum_cap5 <- paste0("<p style = 'width:1280px;'>Cumulative annual precipitation by month for past 5 years (", yr5, ":", yr_current, " ) compared to the 20th century baseline. Total monthly precipitation data are derived from  <a href='https://www.ncei.noaa.gov/access/metadata/landing-page/bin/iso?id=gov.noaa.ncdc:C00332'>NOAA monthly NClimGrid gridded climate data</a> extracted for a given park's geographic centroid.</p>")

drgt_cap5 <- paste0("<p style = 'width:1280px;'>Last 5 years (", yr5, ":", yr_current, ") of weekly drought condition based on proportion of a park's predominant county by drought level using the <a href='https://droughtmonitor.unl.edu/'>U.S. Drought Monitor</a>.</p>") 

temp_capT <- paste0("<p style = 'width:1280px;'>Loess smoothed (span 0.3) minimum, maximum, and average temperature trends from 1900 to ", yr_current, " by month derived from <a href='https://www.ncei.noaa.gov/access/metadata/landing-page/bin/iso?id=gov.noaa.ncdc:C00332'>NOAA NClimGrid </a> gridded climate dataset extracted for a given park's geographic centroid.</p>")

ppt_capT <- paste0("<p style = 'width:1280px;'>Loess smoothed (span 0.3) total precipitation trends by month from 1900 to ", yr_current, " derived from <a href='https://www.ncei.noaa.gov/access/metadata/landing-page/bin/iso?id=gov.noaa.ncdc:C00332'>NOAA NClimGrid </a> gridded climate dataset extracted for a given park's geographic centroid.</p>")

anom_capT <- paste0("<p style = 'width:1280px;'>Monthly deviations from historic baselines, with positive (red) bars, indicated above average deviations, and negative (blue) bars indicating below average deviations for 1900 to ", yr_current, ". Historic baselines are based on <a href='https://www.ncei.noaa.gov/products/land-based-station/us-climate-normals'>NOAA 20th century normals</a> for a given park's geographic centroid. Monthly data are derived from <a href='https://www.ncei.noaa.gov/access/metadata/landing-page/bin/iso?id=gov.noaa.ncdc:C00332'>NOAA NClimGrid </a> gridded climate dataset extracted for a given park's geographic centroid.</p>")

drgt_capT <- paste0("<p style = 'width:1280px;'>Long-term trends (2000:", yr_current, ") in weekly drought condition based on proportion of a park's predominant county by drought level using the <a href='https://droughtmonitor.unl.edu/'>U.S. Drought Monitor</a>. Note that drought data are only available from 2000 to present.</p>") 

```

#### Current Year {.tabset}
<h1>Current vs. 20th Century Baseline</h1>
<details open><summary class='drop'>Temperature</summary>
```{r fig.height=7, fig.width=13, results = 'asis'}
temp_comp <- plotClimComps(park = parkcode, years = yr_current, palette = 'red', parameter = c('tmean'),
                           legend_position = 'bottom', plot_title = F, units = "eng")
temp_anom <- plotClimAnom(park = parkcode, years = yr_current, parameter = 'tmean',
                          legend_position = 'bottom', units = "eng")
grid.arrange(temp_comp, temp_anom, nrow = 1)

cat(anom_comp_cap1, "\n\n")
```

</details>
<br>
<details open><summary class='drop'>Precipitation</summary>
```{r fig.height=7, fig.width=13, results = 'asis'}
ppt_comp <- plotClimComps(park = park,years= yr_current, palette = 'blue', parameter = c('ppt'),
                           legend_position = "bottom", plot_title = F, units = "eng")
ppt_anom <- plotClimAnom(park = parkcode, years = yr_current, parameter = 'ppt_pct',
                          legend_position = "bottom")
grid.arrange(ppt_comp, ppt_anom, nrow = 1)

cat(anom_comp_cap1, "\n\n")
```
</details>
<br>
<details open><summary class='drop'>Drought Condition</summary>
```{r fig.height=7, fig.width=13, results = 'asis'}
drgt <- plotClimDrought(park = parkcode, years = yr_current, legend_position = 'bottom')
pptcum <- plotClimCumPrecip(park = parkcode, years = yr_current, legend_position = "bottom", units = "eng")
cat("\n\n")
grid.arrange(drgt, pptcum, nrow = 1)
cat("\n\n")

cat("\n", drgt_cumppt_cap1, "\n\n")
```
</details>
<br>

#### 5-year Trends {.tabset}
<h1>5-year vs. 20th Century Baseline</h1>
<details open><summary class='drop'>Temperature</summary>
```{r fig.height=8, fig.width=13, results = 'asis'}
yr1 = yr_current - 4
plotClimAnom(park = parkcode, years = yr1:yr_current, parameter = 'tmean', 
             legend_position = "bottom", gridlines = "grid_x", units = "eng")
cat(anom_cap5, "\n\n")
```
</details>
<br>

<details open><summary class='drop'>Total Precipitation</summary>
```{r fig.height=8, fig.width=13, results = 'asis'}
plotClimAnom(park = parkcode, years = yr1:yr_current, parameter = 'ppt_pct', 
             legend_position = "bottom", gridlines = "grid_x")
cat(anom_cap5, "\n\n")
```
</details>
<br>

<details open><summary class='drop'>Cumulative Precipitation</summary>
```{r fig.height=8, fig.width=13, results = 'asis'}
plotClimCumPrecip(park = parkcode, years = yr1:yr_current, legend_position = "bottom", units = "eng")

cat(cum_cap5, "\n\n")

```
</details>
</br>

<details open><summary class='drop'>Drought Condition</summary>
```{r fig.height=8, fig.width=13, results = 'asis'}
plotClimDrought(park = parkcode, years = yr1:yr_current, gridlines = "grid_x", 
                legend_position = "bottom")
cat(drgt_cap5, "\n\n")
```
</details>
</br>

#### Long-term Trends {.tabset}
<h1>Historic Trends 1900:2023</h1>
<details open><summary class='drop'>Temperature Trends</summary>
```{r fig.height=8, fig.width=13, results = "asis"}
plotClimTrend(park = parkcode, years = 1900:yr_current, 
              parameter = c("tmin", "tmax", "tmean"), facet_param = F,
              palette = "Dark2", legend_position = "bottom", plot_se = T,
              layers = "smooth", gridlines = "grid_x", units = "eng")
cat(temp_capT, "\n\n")

```
</details>
<br>

<details open><summary class='drop'>Temperature Anomalies</summary>
```{r fig.height=8, fig.width=13, results = 'asis'}
plotClimAnom(park = parkcode, years = 1900:yr_current, units = "eng", 
              parameter = c("tmean"), legend_position = "bottom", gridlines = "grid_x")

cat(anom_capT, "\n\n")
```
</details>
<br>

<details open><summary class='drop'>Precipitation Trends</summary>
```{r fig.height=8, fig.width=13, results = 'asis'}
plotClimTrend(park = parkcode, years = 1900:yr_current, 
              parameter = c("ppt"), facet_param = F, plot_se = T,
              palette = "Dark2", legend_position = "bottom", 
              layers = "smooth", gridlines = "grid_x", units = "eng")

cat(ppt_capT, "\n\n")
```
</details>
<br>

<details open><summary class='drop'>Precipitation Anomalies</summary>
```{r fig.height=8, fig.width=13, results = 'asis'}
plotClimAnom(park = parkcode, years = 1900:yr_current, gridlines = "grid_x", 
              parameter = c("ppt_pct"), legend_position = "bottom")

cat(anom_capT, "\n\n")
```
</details>
<br>


<details open><summary class='drop'>Drought Conditions</summary>
```{r fig.height=8, fig.width=13, results = 'asis'}
plotClimDrought(park = parkcode, years = 2000:yr_current, gridlines = "grid_x", 
                legend_position = "bottom")

cat(drgt_capT, "\n\n")
```
</details>
<br>

### About the Sites
```{r out.width="80%", message=F}
NPSbasic <- "https://atlas-stg.geoplatform.gov/styles/v1/atlas-user/ck58pyquo009v01p99xebegr9/tiles/256/{z}/{x}/{y}@2x?access_token=pk.eyJ1IjoiYXRsYXMtdXNlciIsImEiOiJjazFmdGx2bjQwMDAwMG5wZmYwbmJwbmE2In0.lWXK2UexpXuyVitesLdwUg"

ESRIimagery <- "http://services.arcgisonline.com/arcgis/rest/services/World_Imagery/MapServer/tile/{z}/{y}/{x}"

ESRItopo <- "http://services.arcgisonline.com/arcgis/rest/services/World_Topo_Map/MapServer/tile/{z}/{y}/{x}"

ESRINatGeo <- "http://services.arcgisonline.com/arcgis/rest/services/NatGeo_World_Map/MapServer/tile/{z}/{y}/{x}"

bbox <- read.csv("boundboxes.csv") #lat/long coordinates and zoom level for each park 

# Find center coordinates of park box
long_cent <- mean(c(bbox$LongE[bbox$ParkCode == park], bbox$LongW[bbox$ParkCode == park]))
lat_cent <- mean(c(bbox$LatN[bbox$ParkCode == park], bbox$LatS[bbox$ParkCode == park]))

# Compile water sites dataframe with codes, names, lat/long coordinates, and site type
water_sites1 <- getSites(park = park)[,c("SiteCode", "SiteName", "SiteLatitude", "SiteLongitude",
                                         "site_type", "SiteDescription")]

years_active <- getEvents(park = parkcode, years = yr_start:yr_current, active = T) |> 
  select(UnitCode, SiteCode, year) |> group_by(UnitCode, SiteCode) |> 
  summarize(year_start = first(year), year_end = last(year), .groups = 'drop')


water_sites <- left_join(water_sites1, years_active, by = c("SiteCode"))
water_sites$Link = paste0("<a href='https://doimspp.sharepoint.com/sites/NETN_Photo_Viewer/Water_Quality_Site_Photos/", 
                     water_sites$Site, ".jpg' target='_blank'>Site Photo</a>")

# Legend html generator
# Source: https://stackoverflow.com/questions/47064921/leaflet-legend-for-addawesomemarkers-function-with-icons
# Icon library changed from font-awesome to ion

markerLegendHTML <- function(IconSet) {
    # Container div:
    legendHtml <- "<div style='padding: 10px; padding-bottom: 10px;'>
    <h4 style='padding-top:0; padding-bottom:10px; margin: 0; color:#555'> Legend </h4>" #legend title

    n <- 1
    # Add each icon for ion library icons:
    for (Icon in IconSet) {
        if (Icon[["library"]] == "ion") {
        legendHtml<- 
          paste0(legendHtml,
          # marker and marker label div
          "<div style='width: auto; height: 45px; display: flex; align-items: center;'>",
          # awesome marker div
          "<div style='position: relative; display: inline-block; width: 35px; height: 45px;' 
          class='awesome-marker-icon-", Icon[["markerColor"]]," awesome-marker'>",
          # add icons and set color
          # class='ion ion-waterdrop icon-white' selects the correct library, icon, and color
          "<i style='margin-left: 4px; margin-top: 11px' class= 'ion ion-",
            Icon[["icon"]]," icon-", Icon[["iconColor"]],"'></i>",
          "</div>", # close awesome marker div
          # legend label div - use name set in IconSet
          "<div style='position: relative; display: inline-block; margin-left: 8px;'>", 
            names(IconSet)[n] ,"</div>",
          "</div>") # close marker/marker label div    
        }
        n <- n + 1
    } 
    paste0(legendHtml, "</div>")
}

# Create list of icons to use in map
IconSet <- awesomeIconList(
  "stream" = makeAwesomeIcon(icon= 'waterdrop', markerColor = 'blue', iconColor = 'white', library = "ion"),
  "lake" = makeAwesomeIcon(icon= 'waterdrop', markerColor = 'cadetblue', iconColor = 'white', library = "ion")
)

# Create leaflet map
leaflet(height = 700) %>%
    # set default view of park
    setView(lng = long_cent,
            lat = lat_cent,
            zoom = bbox$Zoom[bbox$ParkCode == park]) %>%
    # setMaxBounds(lng1 = bbox[bbox$ParkCode == parkcode,]$LongE,
    #              lng2 = bbox[bbox$ParkCode == parkcode,]$LongW,
    #              lat1 = bbox[bbox$ParkCode == parkcode,]$LatN,
    #              lat2 = bbox[bbox$ParkCode == parkcode,]$LatS) %>%
    # add map tiles
    addTiles(group="Map", urlTemplate = NPSbasic, 
             options = providerTileOptions(minZoom = bbox$minZoom[bbox$ParkCode == park])) %>%
    addTiles(group="Imagery", urlTemplate = ESRIimagery) %>%
    addTiles(group="Topo", urlTemplate = ESRItopo) %>%
    addTiles(group="NatGeo", urlTemplate = ESRINatGeo) %>%
    # add button to control map tiles
    addLayersControl(map = ., baseGroups = c("Map","Imagery","Topo", "NatGeo"),
                     options = layersControlOptions(collapsed=T)) %>%
    # add site markers 
    addAwesomeMarkers(data = water_sites, ~SiteLongitude, ~SiteLatitude, 
                      icon = ~IconSet[site_type], #style markers based on site type
                      # label on mouseover
                      label=as.character(water_sites$SiteName),
                      # popup on click
                      popup = paste0("<b>", water_sites$SiteName, "</b><br>",
                                     "<b>Type: </b>", water_sites$site_type, "<br>",
                                     "<b>Sample Period: </b>", water_sites$year_start, "&ndash;",
                                     water_sites$year_end, "<br>",
                                     water_sites$SiteDescription, "<br>",
                                     water_sites$Link
                                     )
                      ) %>%
    # add legend
    addControl(markerLegendHTML(IconSet = IconSet), position = "bottomleft")

```

